Embedded Scalars, Preferred Readings \& Intonation: {A}n Experimental Revisit

### 2015-11-04 text/paper/reviews_2/response_letter.md

1. careful reformulation of conclusions to be drawn from our data in line with reviewer 2's suggestions;

2. shortening of section 3 to remove unnecessary detail in predictions of "core theories";

3. addition of a few elements of emphasis in introduction, Section 4 and reflection section 6, in response to reviewer 2's comments showing that the previous version may not have made the motivation of our design sufficiently clear.

All significant changes from the previous to this version are highlighted in a separately attached PDF.

@@

We tried our very best to address all of the issues raised by reviewer 2, and
paid particular attention to those issues flagged as most important by the
reviewer herself/himself or the editor.

[In the following, we reproduce the full review and use boldface to indicate the aspects that subsequent comments target.]

>The authors have done a good job responding to the first round of feedback. As in the previous round of review, I believe the paper makes a valuable contribution to the literature on scalar strengthening, and that the paper should be published. However, I continue to believe there is room for improvement. Specifically, **I believe the paper can be streamlined by taking fuller advantage of previous results**, which I hope will also clarify the contributions that the paper makes. 
>
>My most important comment, which I'll try to spell out in Section 1 below, is that the question-answer structure of the paper does not come across as cleanly as it should. **To my mind, the paper aims to answer two questions: (i) Are embedded strengthenings licensed only under marked prosody, i.e., is the Prosodic Marking Hypothesis true? (ii) Are there preferences for the different readings predicted by theories of strengthening? If so, what are they, and how are they determined?** 
>
>I believe the paper answers (i) quite nicely, but it burdens the reader with too much irrelevant information in setting up and addressing the question (much of section 3 of the paper up to but not including section 3.3 on the Prosodic Marking Hypothesis). Concerning question (ii), the paper leaves it unresolved, which would be fine had the authors not mischaracterized the question by invoking the Strongest Meaning Hypothesis in the way that they did (as I hope to clarify below). If these issues could be resolved in a revised version, I would have no serious objection to publication.

We are sorry that we didn't specify these points clearly enough in our previous manuscript. We feel that this description of what the paper is about is unfortunately not entirely as we intended. This could lead to certain misunderstandings, so we clarify our position in the present manuscript. We have also modified the text (introduction, especially the relevant Section 4.4, section 6) to strengthen our view of and the motivation for out study.

### 2015-11-04 text/paper/revision_02/title_page/titlePage.tex
this version second revision sent

\begin{abstract}
  The scalar item \emph{some} is widely assumed to receive a meaning
  enrichment to \emph{some but not all} if it occurs in matrix
  position. The question under which circumstances this enrichment can
  occur in certain embedded positions plays an important role in
  deciding how to delineate semantics and pragmatics. % Some claim
  % that it requires marked intonation for the relevant pragmatic
  % enrichment to occur in embedded position; others allow for it more
  % freely.
  We present new experimental data that bear on this theoretical
  issue. In distinction to previous experimental approaches, we
  presented sentence material auditorily in order to explicitly
  control prosodic markedness of the scalar item. Moreover, our
  experiment sheds light on the relative preferences or salience of
  candidate readings. The presented data turn out to be unexpected
  under a traditional Gricean view, but also suggest refinement of the
  more recent grammatical approach.
\end{abstract}

>>>>

\begin{abstract}
  The scalar item \emph{some} is widely assumed to receive a meaning enrichment to \emph{some
    but not all} if it occurs in matrix position. The question under which circumstances this
  enrichment can occur in certain embedded positions plays an important role in deciding how to
  delineate semantics and pragmatics.  We present new experimental data that bear on this
  theoretical issue. In distinction to previous experimental approaches, we presented sentence
  material auditorily in order to explicitly control prosodic markedness of the scalar
  item. Moreover, our experiment sheds light on the relative preferences or salience of
  candidate readings. The presented data turn out to be unexpected under a traditional Gricean
  view, but also challenge the idea of disambiguation by logical strength in grammaticalist
  approaches.
\end{abstract}
